\documentclass[12pt,a4paper]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[scale=0.85]{geometry}

\usepackage[defernumbers=true, sorting=ydnt, maxnames=99]{biblatex}


% \usepackage[bibstyle=publist, plauthorhandling=highlight, plnumbering=local, maxnames=99, ]{biblatex}
% \plauthorname[Sudhanshu]{Tiwari}

\addbibresource{Publication.bib}


\name{Sudhanshu}{Tiwari}
\title{}
\address{AWS Center for Quantum Computing}{Pasadena, CA, USA}
\phone[mobile]{+1-765-775-9255}
\email{sudhanshu\_t@hotmail.com}
\social[linkedin]{sudhanshut}
\social[googlescholar]{user=JUvmVtsAAAAJ\&hl=en}



\begin{document}

\makecvtitle

\vspace{-0.5cm}


\section{Research Experience}

\cventry{2024 -- Current}{Research Scientist II}{Amazon Web Services, Center for Quantum Computing}{Pasadena, CA}{}{
  \begin{itemize}
    \item Leading research on scalable architectures for fault-tolerant quantum computing, with a focus on device physics and system-level integration.
    \item Collaborating with cross-disciplinary teams to translate fundamental research into deployable quantum technologies.
    \item Mentoring junior researchers and contributing to long-term research strategy within the hardware development group.
  \end{itemize}
}

\cventry{2021 -- 2024}{Postdoctoral Research Associate}{Purdue University}{West Lafayette, IN}{}{
  \begin{itemize}
    \item Principal researcher for DARPA MTO WARP and COFFEE programs, driving experimental design, device development, and program deliverables.
    \item Advanced the DARPA COFFEE Program to Phase 2 in collaboration with BAE Systems. 
    \item Hosted and presented program milestones to DARPA program managers and industrial collaborators.
    \item Organized and led weekly research meetings; prepared technical presentations and demonstrations for U.S. government stakeholders.
    \item Co-authored a successful proposal to the U.S. Army Research Laboratory.
    \item Mentored graduate and undergraduate researchers in device fabrication, modeling, and experimental methods.
  \end{itemize}
}

\cventry{2015 -- 2021}{Graduate Researcher}{Indian Institute of Science}{Bengaluru, India}{}{
  \begin{itemize}
    \item Conducted independent research in PiezoMEMS, resulting in multiple journal publications and a patent.
    \item Designed and demonstrated a novel tip-coupled two-cantilever microsystem for viscosity sensing.
    \item Initiated and sustained collaborations with interdisciplinary teams across materials science, microfabrication, and device physics.
  \end{itemize}
}


\section{Teaching and Mentorship Experience}

\cventry{2023 -- 2024}{Instructor of Record}{Purdue University}{West Lafayette, IN}{}{
  \begin{itemize}
    \item Designed and taught a graduate-level course on Microelectromechanical Systems (MEMS).
    \item Achieved a strong student evaluation score: \textbf{4.28/5}.
    \item Nominated by \textit{four} students for the Postdoctoral Mentor Award in recognition of exceptional guidance and support.
  \end{itemize}
}

\cventry{2018}{Teaching Assistant}{Indian Institute of Science}{Bengaluru, India}{}{
  \begin{itemize}
    \item Delivered tutorials on COMSOL Multiphysics for MEMS design and supported students through office hours and assignment evaluations.
  \end{itemize}
}


\section{Education}

\cventry{2011--2015}{Bachelor of Technology}{A.P.J. Abdul Kalam Technical University}{Lucknow, India}{}{Mechanical Engineering}

\cventry{June 2021}{MSc. (Engg.) \& PhD}{Indian Institute of Science}{Bengaluru, India}{Nanoscience and Engineering}{PhD thesis focus in Piezoelectric Microelectromechanical Systems (PiezoMEMS)}


\nocite{*} % Include all publications from the .bib file
\printbibliography[type=patent,title={Patents},resetnumbers=true]
\printbibliography[type=article,title={Journal Publications},resetnumbers=true]
\textbf{* Corresponding/Equally Contributing Author}
\printbibliography[type=inproceedings,title={Conference Publications},resetnumbers=true]

\section{Awards}
\cvitemwithcomment{}{New Employee Recognition Award for Departmental Achievement}{ECE Purdue}
\cvitemwithcomment{}{Nominated by 4 students for the 2024 Postdoctoral Mentor Award}{Purdue}
\cvitemwithcomment{}{Institute Fellowship for Graduate Research}{Through GATE Exam}
\cvitemwithcomment{}{GARP Travel Award}{For conference travel from IISc}
\cvitemwithcomment{}{Travel Grant from IEEE UFFC}{For attending F\textsuperscript{2}C$\pi^2$ 2019 Joint Conference}

\section{Services}
\cventry{2020-Current}{\textbf{Reviewer}}{}{}{}{
\begin{itemize}
    \item \textbf{Nature} Communications
    \item \textbf{IEEE} Sensors Journal
    \item \textbf{IEEE} Microwave and Wireless Technology Letters
    \item \textbf{IOP} Journal of Micromechanics and Microengineering
    \item \textbf{IEEE} Sensors Conference Series
\end{itemize}
}

\cventry{}{\textbf{Outreach}}{}{}{}{
\begin{itemize}
\item Served as the \textbf{Vice-Chair} of the local IEEE chapter at IISc from 2017 to 2018. Secured a competitive grant from the \textbf{IEEE Sensors council} for organizing a Summer School on the theme "Nanotechnology: From Science to Systems and Beyond."
\item Actively participated in organizing several outreach programs such as \textbf{Think Nano} and \textbf{Women in Science and Engineering}.
\item Coordinator and Instructor of fabrication module for Special Workshop on Piezoelectric Micromachined Ultrasound Transducers for NPOL (DRDO) Scientists.
\end{itemize}
}

\section{Grant Writing Experience}
\cvitem{}{Co-authored successful Core Research Grant proposal (SERB, India).}
\cvitem{}{Contributed to funded ARL proposal on MSW loss-study(Funded).}
\cvitem{}{Assisted in proposal development for DARPA HOTS program (funded).}


\section{Invited Talks}

\cvitemwithcomment{Magnetostatic wave filters}{@ IISc, Bengaluru}{Dec 2025}

\cvitemwithcomment{MEMS-Engineered Magnetics: The Future of Agile RF Filtering}{@ UC Davis, USA}{July 2025}

\cvitemwithcomment{Magnetostatic Wave Technology}{@ UT El Paso, USA}{Feb 2024}

\cvitemwithcomment{Materials to Devices: Piezo MEMS}{@ NMIT, Bangalore, India}{Feb 2018}


\end{document}

